---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# horusheresy

<!-- badges: start -->
[![R-CMD-check](https://github.com/Matt-Tansley/horusheresy/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Matt-Tansley/horusheresy/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`horusheresy` is a data package containing data on the Horus Heresy 2.0 rules.

## Installation

Install the package from GitHub like so:

``` r
devtools::install_github("Matt-Tansley/horusheresy")
```

## Usage

This package creates the `horusheresy` data object.

Use `?horusheresy` for more info on the data and its format.

```{r example}
library(horusheresy)

head(horusheresy)
```

## About 

Data comes from the Horus Heresy BattleScribe data files: https://github.com/BSData/horus-heresy-2nd-edition

Specifically, the main rules data file is used: https://github.com/BSData/horus-heresy-2nd-edition/blob/main/2022%20-%20Horus%20Heresy.gst
